---
title: "2DA3_A1"
author: "Jingru Feng"
date: "2023-09-25"
output: pdf_document

---
#Question 1
```{r}
#install.packages('carData')
library(carData)
```
##a)
There are 6 columns and 397 rows in the dataset.
```{r}
#Salaries
colnames(Salaries) #6
rownames(Salaries) #397
```
##b)
'Salary' describes nine-month salary, in dollars in 'Salaries' dataset. 
```{r}
??Salaries
```
##c)
categorical variables: rank, discipline, sex
continuous variables: yrs.since.phd, yrs.service, salary
```{r}
summary(Salaries)
```
##d)
```{r}
#install.packages("ggplot2")
library(ggplot2)

ggplot(Salaries, aes(x=yrs.since.phd, y=salary))+ geom_point(color="red")+labs(title = "Experience vs. Salary", x = "Years Since PhD", y = "Salary")

```
#Question 2
```{r}
#diamonds
```
##a)
```{r}
a <- ggplot(diamonds, aes(x=cut, fill=cut)) + geom_bar()
a
```
##b)
```{r}
b <- ggplot(diamonds, aes(x=cut, fill=clarity)) + geom_bar()
b
```
##c)
```{r}
#install.packages("gridExtra")
library(gridExtra)

grid.arrange(a,b,ncol=2)
```
#Question 3
a) None improvement was the most reported level of Improvement. 
b) Some Imrovement was the least reported level of Improvement. 
c) For female patients in the Treated group showed showed the best (“Marked”) level of Improvement. 

#Question 4
```{r}
mpg <- ggplot2::mpg
mpg
table(mpg$class)
table(mpg$drv)
library(ggplot2)
library(likert)
library(dplyr)
library(tidyr)
library(vcd)
```
##a)
```{r}
doubledecker(drv ~ class, data=mpg, main = "Double Decker plot")
```
##b)f
##c)f
##d)
```{r}
d <- ggplot(mpg, aes(x=class, fill=drv)) + geom_bar()
d
```
