---
title: "2DA3_A2"
author: "Jingru Feng"
date: "2023-10-14"
output: pdf_document
latex_engine: xelatex
---
# Question 1
##a) The best number of clusters to choose is 2.
By the silhouette measures, the highest average silhouette width gives the best k. The average silhouette width of the k=2 cluster is 0.19, which is the largest average in all cases. So, the best number of clusters to choose is 2. 
##b) The worst number of clusters to choose is 5.
By the silhouette measures, the highest average silhouette width gives the best k. From the figures, the average silhouette width of k=5 cluster is 0.09, which is the lowest. So, the worst cluster number is 5.

# Question 2
##a) 
k-means clustering: the cluster centers are means. 
k-medoids clustering: the cluster centers are medoids. 
##b)
No. Because k-means clustering is not the most appropriate. And these three clusters are not spherical whcih means we cannot achieve the optimal clustering results. 

# Question 3
```{r}
#install.packages('s20x')
library(s20x)
data(course.df)
course.df
??course.df
head(course.df)
str(course.df)
```
##a)
```{r}
library(ggplot2)
a <- ggplot(course.df, aes(x= Degree, y= Exam)) + geom_boxplot() + 
    labs(x= "Degree", y= "Exam Score") + theme_minimal()
a

b <- ggplot(course.df, aes(x= Degree, y= Exam, fill= Gender)) +geom_boxplot() +
    labs(x= "Degree", y= "Exam Score") + theme_minimal()
b
```
##b)
```{r}
#install.packages('gridExtra')
library(gridExtra)
grid.arrange(a, b, ncol=1)
```
##c)
```{r}
ggplot(course.df, aes(x= interaction(Degree, Gender), fill= Gender)) + geom_bar() + theme_minimal()
```
##d)
```{r}
#install.packages('GGally')
library(GGally)
ggparcoord(data = course.df, columns = c("Assign", "Test", "B", "C", "MC"), 
           groupColumn = "Grade", order = "allClass", scale = "uniminmax") + theme_minimal()
```
# Question 4
##a)
In my opinion, CaO is the best predictor variable for separating out the responses. Because there is a very clear distinction between Body part and Glaze part.