---
title: "2DA3_A4"
author: "Jingru Feng"
date: "2023-11-14"
output: pdf_document
---
#Question 1
```{r}
set.seed(3456)
sample(1:15,10,replace = TRUE)
sample(1:20,5,replace = FALSE)
x <- rnorm(5)
print(x)
```
#Question 2
##i)We find the top 5 nearest thing of unlabelled observation "x" is "blue circle". Because when K=5 there are 3 "blue circle",1 "yellow star" and 1 "red triangle". "blue circle" is the largest quantity.
##ii)We find the top 9 nearest thing of unlabelled observation "x" is "yellow star". When K=6 there are 3 "yellow star", 3 "blue circle" and 1 "red triangle", whether k=9, the increased observation is 1 star and 1 triangle or 2 stars. In the end, "yellow star" is the largest quantity.

#Question 3
##a)
```{r}
seeds <- read.csv("/Users/fengjingru/Desktop/seeds.csv")
seeds$Class <- as.factor(seeds$Class)
```
##b)
```{r}
library(dplyr)
seeds_scaled <- scale(select(seeds, -Class))
classes <- seeds$Class
```
##c)
```{r}
set.seed(6789)
train_indices <- sample(1:nrow(seeds_scaled), 0.8 * nrow(seeds_scaled))
train_set <- seeds_scaled[train_indices, ]
test_set <- seeds_scaled[-train_indices, ]
actual_classes <- classes[-train_indices]
```
##d)
```{r}
library(class)
predicted_classes <- knn(train = train_set, test = test_set, cl = classes[train_indices], k = 3)
predicted_classes
```
##e)
```{r}
tab1 <- table(Predicted = predicted_classes, Actual = actual_classes)
tab1
```
##f)
```{r}
library(e1071)
classAgreement(tab1)$crand
```
##g)
```{r}
1-classAgreement(tab1)$diag
```
